The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }

### 2017-03-03 paper.tex
about to start on the discussion

\usepackage{hyperref}
\hypersetup{
  colorlinks,
  citecolor=blue,
  linkcolor=red,
  urlcolor=cyan}

@@

% Abstract of the paper
\begin{abstract}
We present dynamical measurements for 77 main sequence star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ from the KMOS (K-band Multi-Object Spectrograph) Deep Survey (KDS).
These measurements constitute the largest sample at $z > 3$ utilising Integral-Field Spectroscopy (IFS), and provide robust constraints on the internal dynamics, via the intrinsic velocity dispersion $\sigma_{int}$ and rotation velocities, $V_{C}$, of galaxies in the high redshift universe.
We have made careful comparisons to other IFS samples which have been selected consistently, span a wide redshift baseline and use ionised gas emission to trace galaxy dynamics. 
The KDS mean dispersion value is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, in agreement with the increase of $\sigma_{int}$ with redshift reported across the comparison samples.
However we find that only $34 \pm 8\%$ of our galaxies are rotationally-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much less than at lower redshift.
The rotation dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e. $V_{C}-M_{\star}$) relation (the inverse of the stellar mass Tully-Fisher relation), although a smaller fraction of the galaxies sit on the relation due to the increase in the dispersion dominated fraction.
The galaxies show a decrease in specific angular momentum (angular momentum divided by stellar mass) of $\sim0.6-0.7$dex in comparison to $z=0$ disk galaxies, with this decline the result of the gradual size evolution of the star-forming population over cosmic time.
Due to these more compact sizes, the KDS galaxies show a paucity of virial mass in comparison to stellar mass, which may be explained through an additional virial component originating in random motions, as traced by $\sigma_{int}$.
These observations are in line with a simple equilibrium model picture, in which random motions are boosted in high redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback.
\end{abstract}

@@

It has been observationally determined that the galaxy population is bimodal in many physical properties at each redshift slice at which it is studied \citep[e.g. as described in][]{Dekel2006}, with a preference for the most massive galaxies to lie in the red sequence, characterised by red optical colours, low Star Formation Rates (SFRs) and spherical morphologies, and less massive galaxies in the blue sequence, characterised by blue colours, high star formation rates and disky morphologies. 
For these blue, star-forming galaxies (SFGs) there is a roughly linear correlation between SFR and stellar mass ($M_{\star}$) \citep[e.g.][]{Daddi2007,Noeske2007,Elbaz2007}, in the sense that galaxies which have already accumulated a larger stellar population tend to have higher SFRs.
This correlation, or `main sequence' underpins what is known as the equilibrium model, in which the SFR of galaxies is regulated by the availability of gas, with outflows and accretion events sustaining the galaxy gas reservoirs in a rough equilibrium as the galaxy evolves \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}.
The main sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sobral2014,Sparre2015,Lee2015,Schreiber2015,Renzini2015,Nelson2016}, finding evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic Star Formation Rate Density (SFRD) in this redshift range \citep{Madau_2014}.
At each redshift slice, galaxies on the main sequence are undergoing secular evolution regulated by their gas reservoirs and so selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
This assumes that high redshift main sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b} and also assumes that we can learn about galaxy evolution (i.e. how individual galaxies develop in physical properties over time) by studying the mean properties of populations at different epochs.
The picture is complicated by the addition of major and minor galaxy mergers which can rapidly change the physical properties of galaxies \citep[e.g.][]{Toomre1977,Lotz2008,Conselice2011,Conselice2014} and the relative importance of in-situ, secular stellar mass growth vs. stellar mass aggregation via mergers is the subject of much work involving both observations and simulations \citep[e.g.][]{Robaina2009,Kaviraj2012,Stott2013,Lofthouse2016,Qu2016}. 
To account for the growing number density of quiescent galaxies from z$\sim 2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be some process which shuts off star-formation within main sequence galaxies (i.e. quenching) which, to explain observations, is a function of both mass and environment \citep{Peng2010,Darvish2016}.

@@

SFGs generally appear to be increasing in random motions with increasing redshift between $0 < z < 3$, as traced by their observed velocity dispersions, $\sigma_{obs}$ \citep{Genzel2008,ForsterSchreiber2009,Law2009,Cresci2009,Gnerucci2011,Epinat2012,Kassin2012,Green2014,Wisnioski2015,Stott2016}.
This has been explained in terms of increased `activity' in galaxies during and before the global peak in cosmic SFRD \citep{Madau_2014}, in the form of higher specific star formation rates (sSFR) \citep{Wisnioski2015}, larger gas reservoirs \citep{Law2009,ForsterSchreiber2009,Wisnioski2015,Stott2016}, more efficient accretion \citep{Law2009}, increased stellar feedback from supernovae \citep{Kassin2012} and turbulent disk instabilities \citep{Law2009,Bournaud2007,Bournaud2016}, all of which combine to increase $\sigma_{obs}$ and complicate its interpretation.
There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Swinbank2012,Tiley2016a,Harrison2017}.
In both cases, systematic differences in measurement and modelling techniques at high redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.

In this paper we present results from the KMOS Deep Survey (KDS), which is a guaranteed time programme focussing on the spatially resolved properties of main sequence SFGs at $z\sim3.5$, a time when the universe was building to peak activity.
There are still many open questions which we can begin to answer by studying the emission from regions of ionised gas within individual galaxies at these redshifts.
For example: \textbf{(1)} How do the physical conditions of the ISM such as electron density and ionisation parameter change as a function of spatial position within the galaxy, and what does this tell us about the application of strong line metallicity calibrators at high redshift?
\textbf{(2)} What are the radial gradients in metal enrichment within these galaxies and what can this tell us about the physical mechanisms responsible for redistributing metals?
\textbf{(3)} What are the dynamical properties of main sequence galaxies at this early stage in their lifetimes? 
\textbf{(4)} What is the connection between the gas phase metallicity and  kinematics, particularly in terms of inflows and outflows of material?

@@

\section{SURVEY DESCRIPTION, SAMPLE SELECTION AND OBSERVATIONS}\label{sec:Survey_and_data}
\subsection{The KDS survey description and sample selection}\label{subsec:survey_intro}
The KDS is a KMOS study of the gas kinematics and metallicity in 77 SFGs with a median redshift of $z\sim3.5$, probing a representative section of the galaxy main sequence.
The addition of this data approximately triples the number of galaxies observed in IFS at this redshift \citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011}, and will allow for a statistically significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution. 
The two key science goals of the KDS are to investigate the resolved kinematic properties of high redshift galaxies in the epoch of galaxy formation, particularly the fraction of rotating disks, the degree of disk turbulence and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
We seek to probe both a `FIELD' environment in which the density of galaxies is typical for this redshift and `CLUSTER' environment containing a known galaxy over-density, in order to gauge the role of environment in determining the kinematics and metallicities of SFGs during this early stage in their formation history.
To achieve this we require very deep exposure times in excess of 7 hours on source to reach the S/N required to detect line emission in the outskirts of the galaxies where the rotation curves begin to flatten and to achieve adequate S/N across several ionised emission lines within individual spatial pixels (spaxels).
Consequently, this is some of the deepest spectroscopic data available for this redshift.

@@

\subsubsection{SSA22}\label{subsubsec:sample_selection_ssa}
A single CLUSTER environment pointing (SSA22-P1; see table \ref{tab:pointings}) is selected from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an overdensity of LBG candidates at $z \sim 3.09$.
Thousands of spectroscopic redshifts have been confirmed for these LBGs with follow up observations using LRIS \citep{Shapley2003,Nestor2013}.
A combination of deep {\em B,V,R} band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011} and archival {\em HST} ACS and WFC3 provides ancillary data in excellent support of integral field spectroscopy, albeit over a shorter wavelength baseline and with shallower exposures than in the GOODS-S field.
Fortunately at $z \sim 3.09$ the [O~{\sc III}]$\lambda$5007 line is shifted into a region of the K-band which is free from OH features and so for the CLUSTER environment pointing we fill the KMOS IFUs with galaxies located towards the centre of the SSA22 protocluster (SSA22-P1).

@@

\subsubsection{Data reduction}\label{subsubsec:datareduction}
The data reduction process relied heavily upon the Software Package for Astronomical Reduction with KMOS, (SPARK; \cite{Davies2013}), implemented using the ESO Recipe Execution Tool (ESOREX) \citep{Freudling2013}.
In addition to the SPARK recipes, custom python scripts were run at different stages of the pipeline and will be described throughout this section.

The SPARK recipes are then used to create dark frames, flatfield, illumination correct and wavelength calibrate the raw data.
An additional step which is not part of the standard reduction process is carried out at this stage, which is to address readout channel bias.
Differences in the readout process across each 64 pixel wide channel on the detector image lead to difference flux baselines in these channels, which are carried through to subsequent reduction stages.
We correct back to a uniform flux baseline across each detector image for each object exposure by identifying pixels which are not illuminated in every readout channel and subtracting the median value of these pixels.
Standard star observations were carried out on the same night as the science observations and are processed in an identical manner to the science data.
Following this pre-processing, each of the object exposures is reconstructed independently, using the closest sky exposure for subtraction, to give more control over the construction of the final stacks for each target galaxy.
Each 300s exposure is reconstructed into a datacube with interpolated $0.1\times0.1^{\prime\prime}$ spaxel size, facilitated by the subpixel dither pattern discussed in \cref{subsubsec:Obs} which boosts the effective pixel scale of the observations. \\

@@

We stack all 300s exposures for each galaxy which pass the sky-subtraction and seeing criteria using 3 sigma-clipping, leaving us with a flux and wavelength calibrated datacube for every object in the KDS sample.
We have found that the thermal background is often under-subtracted across the spatial extent of the cube following a first pass through the pipeline, leading to excess flux towards the long wavelength end of the K-band.
To account for this a polynial function is fit, using the python package {\tt LMFIT} \citep{Newville2014} which makes use of the Levenberg-Marquardt algorithm for non-linear curve fitting, to the median stacked spectrum from spaxels in the datacube which contain no object flux and then subtracted from each spaxel in turn. \\

@@

\subsubsection{SED fitting and main sequence}\label{subsubsec:sed_fitting}
We use SED modelling to constrain simultaneously the $M_{\star}$ and SFR of the KDS targets.
During the SED modelling we assume solar metallicity stellar templates, and make use of \cite{Calzetti2000} reddening law with exponentially declining SFRs in both GOODS-S and SSA22.
We have also computed the quantities using 0.2Z$\odot$ templates, finding stellar masses for the galaxies which are on average 0.1 dex lower, but this change does not affect the conclusions of this work.
The median stellar mass for the full observed samples in both GOODS-S and SSA22 is $log(M_{\star}[M_{\odot}]) = 10.0$.
In SSA22 29 targets (36\% of the full KDS sample) do not have SFR measurements due to having J and K-band detections lower than 2-$\sigma$ significance.
For these objects we are able to estimate robust stellar masses from the available photometry, noting that the median of stellar mass distribution is $\sim 0.3$ dex lower than the median stellar mass in GOODS-S.
In figure \ref{fig:main_sequence} we plot the M$_{\star}$ and SFR `main sequence' for the 64\% of KDS galaxies with SFR measurements, in combination with the derived physical properties of $\sim 10,000$ SFGs at $2.5 < z < 3.5$  (based upon the `z\_best classification flag') from the 3D-{\em HST} survey \citep{Brammer2012,Momcheva2016}.
We also plot both the linear-break and quadratic $z\sim 2.5$ main sequence fits to the 3D-{\em HST} data described in \cite{Whitaker2014} with the solid and dashed black lines as well as the MS relation described in \cite{Speagle2014} given in equation \ref{eq:speagle_ms}, evaluated at $z\sim3.5$ where the age of the universe is 1.823 Gyr, with the green line.

@@

The difference in position of these relations highlights the MS evolution towards higher SFRs at fixed $M_{\star}$ between $z\sim2.5-3.5$.
The KDS galaxies scatter, within the errors, consistently above and below the z$\sim3$ main sequence, indicating that they represent typical SFGs at this redshift.

\subsubsection{Sample summary}\label{subsubsec:sample_summary}
We have observed 77 SFGs spanning $3.0 < z < 3.8$ with the KMOS IFUs as part of the KMOS Deep Survey and have derived $M_{\star}$ values and SFRs from SED modelling.
Three KMOS pointings cover the field environment, and one pointing covers a cluster environment at the heart of the SSA22 protocluster and with these data we seek gauge the role of environment in shaping the early evolutionary history of SFGs.
Throughout the following analysis sections we describe the use of high-resolution imaging to make morphological measurements for the KDS galaxies and the extraction of kinematic properties for the galaxies using the [O~{\sc III}]$\lambda$5007 emission line.
Chemical abundance measurements for the KDS galaxies in both the field and cluster environments will be presented in a future work.

@@

\subsection{Morphological Measurements}\label{subsec:morphological_measurements}
For a robust interpretation of the observed velocity fields, it is necessary to separately determine the morphological properties of the galaxies from high-resolution images.
This imaging is used primarily to determine morphological parameters which characterise the size (quantified here through the half-light radius, $R_{1/2}$,), morphological position angle, $PA_{morph}$, and axis ratio, $b/a$, of the galaxies. 
In the following sections we describe the approach we have chosen to recover these parameters detailing comparisons with matched galaxies in the morphological parameter catalogue of \cite{VanderWel2012}.
At $3 < z < 4$ and $0.1 < z < 1$ we have made use of secure spectroscopic redshifts obtained for SFGs during the ESO public surveys zCOSMOS \citep{Lilly2007}, VUDS \citep{Tasca2016}, GOODS\_FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and GOODS\_VIMOS \citep{Balestra2010} to cross-match with \cite{VanderWel2012}.
This allows us to look at the morphological properties of typical SFG populations at two redshift slices in comparison with those determined for the KDS sample.
The imaging also helps to distinguish multiple `merging' components with small angular separations from objects which are morphologically isolated, which we discuss in \cref{subsubsection:spaxel_fitting} and \cref{subsec:morpho-kin-class} where we refine our sample for dynamical analysis.

@@

We first run SExtractor \citep{Bertin1996} on the relevant images to recover initial input parameters and segmentation maps for running {\tt GALFIT} and then extract postage stamp regions around the galaxies in the KDS sample.
At this redshift, the galaxies are more compact and generally we cannot resolve more complicated morphological features such as spiral arms and bars and so we follow the simple method of fitting \Sers profiles, with the \Sers index fixed to the exponential disk value of n = 1.
During the fitting process all other morphological parameters, including $R_{1/2}$, the central x and y coordinates, $PA_{morph}$ and inclination, are free to vary.
This method has been verified in GOODS-S by comparing the $\chi ^{2}$ recovered from fitting floating \Sers index models, bulge/disk models with both an n = 1 and n = 4 component and from the fixed exponential disk value of n = 1 following the procedure described in \cite{Bruce2012}, with the median ratio of $\chi ^{2}$ $\sim 1$ between the different fitting methods. Additionally 22 GOODS-S objects are also detected in the \cite{VanderWel2012} catalogue the median \Sers index value is n = 1.2.
The use of exponential profiles also facilitates comparison with recent large surveys such as KMOS$^{3D}$ \citep{Wisnioski2015} and KROSS \citep{Harrison2017} in which beam-smearing correction factors are applied to the derived kinematic parameters as a function of exponential disk scale length, $R_{D}$, defined as $R_{1/2} \sim 1.68 R_{D}$ (see \cref{subsec:KROSS}). \\

In the F160W band the adopted PSF is a hybrid between the Tiny Tim H-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the H-band for the wings \citep{VanderWel2012} and in the F814W band we use the pure Tiny Tim ACS high-resolution PSF model.

>>>>

\usepackage[draft]{hyperref}
\hypersetup{
  colorlinks,
  citecolor=blue,
  linkcolor=red,
  urlcolor=cyan}

@@

% Abstract of the paper
\begin{abstract}
We present dynamical measurements for 77 main sequence star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ from the KMOS (K-band Multi-Object Spectrograph) Deep Survey (KDS).
These measurements constitute the largest sample at $z > 3$ utilising Integral-Field Spectroscopy (IFS), and provide robust constraints on the internal dynamics, via the intrinsic velocity dispersion $\sigma_{int}$ and rotation velocities, $V_{C}$, of galaxies in the high-redshift universe.
We have made careful comparisons to other IFS samples which have been selected consistently, span a wide redshift baseline and use ionised gas emission to trace galaxy dynamics. 
The KDS mean dispersion value is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, in agreement with the increase of $\sigma_{int}$ with redshift reported across the comparison samples.
However we find that only $34 \pm 8\%$ of our galaxies are rotationally-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much less than at lower redshift.
The rotation dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e. $V_{C}-M_{\star}$) relation (the inverse of the stellar mass Tully-Fisher relation), although a smaller fraction of the galaxies sit on the relation due to the increase in the dispersion dominated fraction.
The galaxies show a decrease in specific angular momentum (angular momentum divided by stellar mass) of $\sim0.6-0.7$dex in comparison to $z=0$ disk galaxies, with this decline the result of the gradual size evolution of the star-forming population over cosmic time.
Due to these more compact sizes, the KDS galaxies show a paucity of virial mass in comparison to stellar mass, which may be explained through an additional virial component originating in random motions, as traced by $\sigma_{int}$.
These observations are in line with a simple equilibrium model picture, in which random motions are boosted in high-redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback.
\end{abstract}

@@

It has been observationally determined that the galaxy population is bimodal in many physical properties at each redshift slice at which it is studied \citep[e.g. as described in][]{Dekel2006}, with a preference for the most massive galaxies to lie in the red sequence, characterised by red optical colours, low Star Formation Rates (SFRs) and spherical morphologies, and less massive galaxies in the blue sequence, characterised by blue colours, high star formation rates and disky morphologies. 
For these blue, star-forming galaxies (SFGs) there is a roughly linear correlation between SFR and stellar mass ($M_{\star}$) \citep[e.g.][]{Daddi2007,Noeske2007,Elbaz2007}, in the sense that galaxies which have already accumulated a larger stellar population tend to have higher SFRs.
This correlation, or `main sequence' underpins what is known as the equilibrium model, in which the SFR of galaxies is regulated by the availability of gas, with outflows and accretion events sustaining the galaxy gas reservoirs in a rough equilibrium as the galaxy evolves \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}.
The main sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sobral2014,Sparre2015,Lee2015,Schreiber2015,Renzini2015,Nelson2016}, finding evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic Star Formation Rate Density (SFRD) in this redshift range \citep{Madau_2014}.
At each redshift slice, galaxies on the main sequence are undergoing secular evolution regulated by their gas reservoirs and so selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
This assumes that high-redshift main sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b} and also assumes that we can learn about galaxy evolution (i.e. how individual galaxies develop in physical properties over time) by studying the mean properties of populations at different epochs.
The picture is complicated by the addition of major and minor galaxy mergers which can rapidly change the physical properties of galaxies \citep[e.g.][]{Toomre1977,Lotz2008,Conselice2011,Conselice2014} and the relative importance of in-situ, secular stellar mass growth vs. stellar mass aggregation via mergers is the subject of much work involving both observations and simulations \citep[e.g.][]{Robaina2009,Kaviraj2012,Stott2013,Lofthouse2016,Qu2016}. 
To account for the growing number density of quiescent galaxies from z$\sim 2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be some process which shuts off star-formation within main sequence galaxies (i.e. quenching) which, to explain observations, is a function of both mass and environment \citep{Peng2010,Darvish2016}.

@@

SFGs generally appear to be increasing in random motions with increasing redshift between $0 < z < 3$, as traced by their observed velocity dispersions, $\sigma_{obs}$ \citep{Genzel2008,ForsterSchreiber2009,Law2009,Cresci2009,Gnerucci2011,Epinat2012,Kassin2012,Green2014,Wisnioski2015,Stott2016}.
This has been explained in terms of increased `activity' in galaxies during and before the global peak in cosmic SFRD \citep{Madau_2014}, in the form of higher specific star formation rates (sSFR) \citep{Wisnioski2015}, larger gas reservoirs \citep{Law2009,ForsterSchreiber2009,Wisnioski2015,Stott2016}, more efficient accretion \citep{Law2009}, increased stellar feedback from supernovae \citep{Kassin2012} and turbulent disk instabilities \citep{Law2009,Bournaud2007,Bournaud2016}, all of which combine to increase $\sigma_{obs}$ and complicate its interpretation.
There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Swinbank2012,Tiley2016a,Harrison2017}.
In both cases, systematic differences in measurement and modelling techniques at high-redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.

In this paper we present results from the KMOS Deep Survey (KDS), which is a guaranteed time programme focussing on the spatially resolved properties of main sequence SFGs at $z\sim3.5$, a time when the universe was building to peak activity.
There are still many open questions which we can begin to answer by studying the emission from regions of ionised gas within individual galaxies at these redshifts.
For example: \textbf{(1)} How do the physical conditions of the ISM such as electron density and ionisation parameter change as a function of spatial position within the galaxy, and what does this tell us about the application of strong line metallicity calibrators at high-redshift?
\textbf{(2)} What are the radial gradients in metal enrichment within these galaxies and what can this tell us about the physical mechanisms responsible for redistributing metals?
\textbf{(3)} What are the dynamical properties of main sequence galaxies at this early stage in their lifetimes? 
\textbf{(4)} What is the connection between the gas phase metallicity and  kinematics, particularly in terms of inflows and outflows of material?

@@

\section{SURVEY DESCRIPTION, SAMPLE SELECTION AND OBSERVATIONS}\label{sec:Survey_and_data}
\subsection{The KDS survey description and sample selection}\label{subsec:survey_intro}
The KDS is a KMOS study of the gas kinematics and metallicity in 77 SFGs with a median redshift of $z\sim3.5$, probing a representative section of the galaxy main sequence.
The addition of this data approximately triples the number of galaxies observed in IFS at this redshift \citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011}, and will allow for a statistically significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution. 
The two key science goals of the KDS are to investigate the resolved kinematic properties of high-redshift galaxies in the epoch of galaxy formation, particularly the fraction of rotating disks, the degree of disk turbulence and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
We seek to probe both a `FIELD' environment in which the density of galaxies is typical for this redshift and `CLUSTER' environment containing a known galaxy over-density, in order to gauge the role of environment in determining the kinematics and metallicities of SFGs during this early stage in their formation history.
To achieve this we require very deep exposure times in excess of 7 hours on source to reach the S/N required to detect line emission in the outskirts of the galaxies where the rotation curves begin to flatten and to achieve adequate S/N across several ionised emission lines within individual spatial pixels (spaxels).
Consequently, this is some of the deepest spectroscopic data available for this redshift.

@@

\subsubsection{SSA22}\label{subsubsec:sample_selection_ssa}
A single CLUSTER environment pointing (SSA22-P1; see table \ref{tab:pointings}) is selected from the SSA22 field, \citep{Steidel1998,Steidel2000,Steidel2003,Shapley2003}, which, as mentioned above, is an overdensity of LBG candidates at $z \sim 3.09$.
Thousands of spectroscopic redshifts have been confirmed for these LBGs with follow up observations using LRIS \citep{Shapley2003,Nestor2013}.
A combination of deep {\em B,V,R} band imaging with the Subaru Suprime-Cam \citep{Matsuda2004}, deep narrow band imaging at 3640$\AA$ \citep{Matsuda2004} and at 4977$\AA$ \citep{Nestor2011} and archival {\em HST ACS} and {\it WFC3} provides ancillary data in excellent support of integral field spectroscopy, albeit over a shorter wavelength baseline and with shallower exposures than in the GOODS-S field.
Fortunately at $z \sim 3.09$ the [O~{\sc III}]$\lambda$5007 line is shifted into a region of the K-band which is free from OH features and so for the CLUSTER environment pointing we fill the KMOS IFUs with galaxies located towards the centre of the SSA22 protocluster (SSA22-P1).

@@

\subsubsection{Data reduction}\label{subsubsec:datareduction}
The data reduction process primarly makes use of the Software Package for Astronomical Reduction with KMOS, (SPARK; \cite{Davies2013}), implemented using the ESO Recipe Execution Tool (ESOREX) \citep{Freudling2013}.
In addition to the SPARK recipes, custom python scripts were run at different stages of the pipeline and will be described throughout this section.

The SPARK recipes are used to create dark frames, flatfield, illumination correct and wavelength calibrate the raw data.
An additional step which is not part of the standard reduction process is carried out at this stage, which is to address readout channel bias.
Differences in the readout process across each 64 pixel wide channel on the detector image lead to a varying flux baselines in these channels.
We correct back to a uniform flux baseline across the detector image for each object exposure by identifying pixels which are not illuminated in every readout channel and subtracting their median value from the rest of the pixels in the channel.

Standard star observations were carried out on the same night as the science observations and are processed in an identical manner to the science data.
Following this pre-processing, each of the object exposures is reconstructed independently, using the closest sky exposure for subtraction, to give more control over the construction of the final stacks for each target galaxy.
Each 300s exposure is reconstructed into a datacube with interpolated $0.1\times0.1^{\prime\prime}$ spaxel size, facilitated by the subpixel dither pattern discussed in \cref{subsubsec:Obs} which boosts the effective pixel scale of the observations. \\

@@

We stack all 300s exposures for each galaxy which pass seeing criteria using 3 sigma-clipping, leaving us with a flux and wavelength calibrated datacube for every object in the KDS sample.
We have found that the thermal background is often under-subtracted across the spatial extent of the cube following a first pass through the pipeline, leading to excess flux towards the long wavelength end of the K-band.
To account for this a polynial function is fit, using the python package {\tt LMFIT} \citep{Newville2014} which makes use of the Levenberg-Marquardt algorithm for non-linear curve fitting, to the median stacked spectrum from spaxels in the datacube which contain no object flux and then subtracted from each spaxel in turn. \\

@@

\subsubsection{SED fitting and main sequence}\label{subsubsec:sed_fitting}
We use SED modelling to constrain simultaneously the $M_{\star}$ and SFR of the KDS targets.
During the SED modelling we assume solar metallicity stellar templates and make use of \cite{Calzetti2000} reddening law with exponentially declining SFRs in both GOODS-S and SSA22.
We have also computed the quantities using 0.2Z$\odot$ templates, finding stellar masses for the galaxies which are on average 0.1 dex lower, but this change does not affect the conclusions of this work.
The median stellar mass for the full observed samples in both GOODS-S and SSA22 is $log(M_{\star}[M_{\odot}]) = 10.0$.
In SSA22 29 targets (36\% of the full KDS sample) do not have SFR measurements due to having J and K-band detections lower than 2-$\sigma$ significance.
For these objects we are able to estimate robust stellar masses from the available photometry, noting that the median of stellar mass distribution is $\sim 0.3$ dex lower than the median stellar mass in GOODS-S.
In figure \ref{fig:main_sequence} we plot the M$_{\star}$ and SFR `main sequence' for the 64\% of KDS galaxies with SFR measurements, in combination with the derived physical properties of $\sim 10,000$ SFGs at $2.5 < z < 3.5$  (based upon the `z\_best classification flag') from the 3D-{\em HST} survey \citep{Brammer2012,Momcheva2016}.
We also plot both the linear-break and quadratic $z\sim 2.5$ main sequence fits to the 3D-{\em HST} data described in \cite{Whitaker2014} with the solid and dashed black lines as well as the main sequence relation described in \cite{Speagle2014} given in equation \ref{eq:speagle_ms}, evaluated at $z\sim3.5$ where the age of the universe is 1.823 Gyr, with the green line.

@@

The difference in position of these relations highlights the main sequence evolution towards higher SFRs at fixed $M_{\star}$ between $z\sim2.5-3.5$.
The KDS galaxies scatter, within the errors, consistently above and below the z$\sim3$ main sequence, indicating that they represent typical SFGs at this redshift.

\subsubsection{Sample summary}\label{subsubsec:sample_summary}
We have observed 77 SFGs spanning $3.0 < z < 3.8$ with the KMOS IFUs as part of the KMOS Deep Survey and have derived $M_{\star}$ values and SFRs from SED modelling.
Three KMOS pointings cover the field environment and one pointing covers a cluster environment at the heart of the SSA22 protocluster and with these data we seek gauge the role of environment in shaping the early evolutionary history of SFGs.
Throughout the following analysis sections we describe the use of high-resolution imaging to make morphological measurements for the KDS galaxies and the extraction of kinematic properties for the galaxies using the [O~{\sc III}]$\lambda$5007 emission line.
Chemical abundance measurements for the KDS galaxies in both the field and cluster environments will be presented in a future work.

@@

\subsection{Morphological Measurements}\label{subsec:morphological_measurements}
For a robust interpretation of the observed velocity fields, it is necessary to separately determine the morphological properties of the galaxies from high-resolution images.
This imaging is used primarily to determine morphological parameters which characterise the size (quantified here through the half-light radius, $R_{1/2}$,), morphological position angle, $PA_{morph}$, and axis ratio, $b/a$, of the galaxies. 
In the following sections we describe the approach we have chosen to recover these parameters detailing comparisons with matched galaxies in the morphological parameter catalogue of \cite{VanderWel2012}.
At $3 < z < 4$ and $0.1 < z < 1$ we have made use of secure spectroscopic redshifts obtained for SFGs during the ESO public surveys zCOSMOS \citep{Lilly2007}, VUDS \citep{Tasca2016}, GOODS\_FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and GOODS\_VIMOS \citep{Balestra2010} to cross-match with \cite{VanderWel2012}.
This allows us to look at the morphological properties of typical star-forming galaxy populations at two redshift slices in comparison with those determined for the KDS sample.
The imaging also helps to distinguish multiple `merging' components with small angular separations from objects which are morphologically isolated, which we discuss in \cref{subsubsection:spaxel_fitting} and \cref{subsec:morpho-kin-class} where we refine our sample for dynamical analysis.

@@

We first run SExtractor \citep{Bertin1996} on the relevant images to recover initial input parameters and segmentation maps for running {\tt GALFIT} and then extract postage stamp regions around the galaxies in the KDS sample.
At this redshift, the galaxies are more compact and generally we cannot resolve more complicated morphological features such as spiral arms and bars and so we follow the simple method of fitting \Sers profiles, with the \Sers index fixed to the exponential disk value of n = 1.
In the F160W band the adopted PSF is a hybrid between the Tiny Tim H-band model \citep{Krist2011} in the PSF centre and an empirical stack of stars observed in the H-band for the wings \citep{VanderWel2012} and in the F814W band we use the pure Tiny Tim ACS high-resolution PSF model.
During the fitting process all other morphological parameters, including $R_{1/2}$, the central x and y coordinates, $PA_{morph}$ and inclination, are free to vary.

This method has been verified in GOODS-S by comparing the $\chi ^{2}$ recovered from fitting floating \Sers index models, bulge/disk models with both an n = 1 and n = 4 component and from the fixed exponential disk value of n = 1 following the procedure described in \cite{Bruce2012}, with the median ratio of $\chi ^{2}$ $\sim 1$ between the different fitting methods. Additionally, 22 GOODS-S objects are also detected in the \cite{VanderWel2012} catalogue, for which the median \Sers index value is n = 1.2.
The use of exponential profiles also facilitates comparison with recent large surveys such as KMOS$^{3D}$ \citep{Wisnioski2015} and KROSS \citep{Harrison2017} in which beam-smearing correction factors are applied to the derived kinematic parameters as a function of exponential disk scale length, $R_{D}$, defined as $R_{1/2} \sim 1.68 R_{D}$ (see \cref{subsec:KROSS}). \\

This analysis provides us with three crucial morphological parameters required to support the kinematic analysis of \cref{subsec:3d_modelling}, namely the axis ratio $b/a$, half-light radius $R_{1/2}$ and the morphological position angle $PA_{morph}$.
Example {\em HST} images and {\tt GALFIT} outputs are given in figure \ref{fig:main_body_kinematic_grids} for selected galaxies, with the full spatially resolved sample (see \cref{subsubsection:spaxel_fitting}) plotted throughout \cref{app:kinematics_plots}.
